\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[french, english]{babel}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage{layout}
\usepackage{fancyhdr}
\usepackage{amssymb,amsmath}
\usepackage{float}
\usepackage{color}
\usepackage{listings}
\usepackage{cite}
\usepackage{url}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\textheight=10in
\pagestyle{empty}
\raggedright
% Margins
\setlength{\headheight}{0pt}
\setlength{\marginparsep}{0pt}
\setlength{\marginparwidth}{0pt}
\setlength{\headsep}{10pt}
\setlength{\footskip}{0pt}
\setlength{\oddsidemargin}{0pt}
\setlength{\evensidemargin}{0pt}
\setlength{\topmargin}{0pt}
\setlength{\textheight}{713pt}
\setlength{\textwidth}{510pt}
\setlength{\hoffset}{-0.15cm}
\setlength{\voffset}{-60pt}
\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1} #2 \end{verse} }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\ }}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}\\
#2
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}
\newcommand{\schoolwithcourses}[4]{
\textbf{#1} #2 $\bullet$ #3\\
#4 $\bullet$ Selected Coursework:\\
\vspace*{5pt}
}
\newcommand{\school}[4]{
\textbf{#1} #2 $\bullet$ #3\\
#4 \\
}
% END RESUME DEFINITIONS
\begin{document}
\urlstyle{sf}
\newpage
\normalsize
\smallskip
\contact{\textsc{\textbf{Johan Hardy}}}
{\textbf{Project Manager} \\
4050 Chaudfontaine (Belgium). \\
+32497197025 -- \href{mailto:hardy.johan@gmail.com}{\nolinkurl{hardy.johan@gmail.com}}}

\header{Education}
2009 : Master in Engineering Science (Graduated with high honors) - Gramme Institute, Liège, Belgium.
\hspace*{0.95cm} \textit{Section :} Industrial Science / Industry. \\
2003 : Secondary School Certificate - Collège Saint Joseph, Liège Belgium. \\
\hspace*{0.95cm} \textit{Orientation :} Latin, Mathematics, English and Dutch.
\vspace{0.3cm}

\header{Work History}
2020 - Today : Spacebel S.A. - Project Manager. \\
2017 - 2020 : Spacebel S.A. - Senior Software Engineer / Technical leader. \\
2009 - 2017 : Spacebel S.A. - Software Engineer. \\
2009 : Internship at Montefiore Institute (Department of Electrical Engineering and Computer Science, \\
\hspace*{0.95cm} University of Liège). \\
\hspace*{0.95cm} \textit{Master thesis :} Implementation of the AX.25 protocol aboard the nanosatellite OUFTI-1\\
\hspace*{0.95cm} (\url{http://www.oufti.ulg.ac.be}). \\
2006 : Social and technical trainee at the National Railway Company of Belgium (SNCB), Atelier de traction \\
\hspace*{0.95cm} Kinkempois (maintenance of rolling stock), Liège,Belgium.
\vspace{0.3cm}

\header{Languages}
French (mother language) \\
English (B2/C1 - Advanced) \\
Dutch (A1 - Basic) \\
\vspace{0.3cm}

\header{Computer Skills}
Microsoft Office, Eclipse, Papyrus, Jenkins CI, svn, git, GitLab, Redmine, VMware, Klocwork, DOORS. \\
C/C++, Java, Tcl/Tk, Python, OCL, UML, Acceleo, EMF, Xtext, Maven, Xtend, Ruby, markup languages. \\
Mocking, MatLab, SimuLink, Eclipse Plug-in development. \\
Sparc LEON2, LEON3, LEON4, PowerPC, Core8051. \\
Unix Systems, VxWorks, RTEMS, Xtratum. \\
\vspace{0.3cm} \header{Additional Training}
2017 : Project Management (PMI/Prince), Bruxelles, Belgium \\
2016 : Spacecraft Techniques and Technology CNES, Toulouse, France \\
2013 : Eclipse Modeling by Olivier Provoust at Spacebel, Liège, Belgium \\
2012 : Xtratum seminar by FentISS at Spacebel, Liège, Belgium \\
2012 : Topcased le résumé at Atos, Paris, France \\
2011 : TargetLink basics for code generation and production in space industry at dSpace, Paris, France \\
2008 : Seminar Espace Horizon Qualité organized by Entreprise \& Qualité ASBL at Technifutur, Sart-Tilman, \\
\hspace*{0.95cm} Belgium.

\vspace{0.3cm}
\header{Miscellaneous}
Belgian nationality. \\
Date of birth: 13rd November 1985. \\
Marital status: married. \\
Driving licence owner (2004). \\
Military Clearance Owner (valid until Nov. 2025) \\
Hobbies: soccer, mountain bike, cinema, music, computer science, electronics, news and politics.

\newpage
\vspace{0.3cm} \header{Professional Experience}
2020 - Today : Spacebel S.A. - Project Manager \\
\hspace*{0.6cm} - Project Management and technical leader of the On-Board Software of In Orbit Demonstrator (IOD) \\
\hspace*{0.6cm} - Project Management ad interim of HERA Central Software \\
\hspace*{0.6cm} - Project Management and technical leader of the On-Board Software of ALTIUS \\
\vspace{0.3cm}
2017 - 2020 : Spacebel S.A. - Senior Software Engineer / Technical leader \\
\hspace*{0.6cm} - Technical leader of Euclid Central Application Software \\
\hspace*{0.6cm} - Development and design of Euclid Central Application Software \\
\vspace{0.3cm}
2009 -- 2017 : Spacebel S.A. - Software Engineer \\
\hspace*{0.6cm} - Development and design of Euclid flight software configuration database \\
\hspace*{0.6cm} - Development and test of PROBA-3 flight software \\
\hspace*{0.6cm} - Design and deployment of PROBA-3 Unit Test framework \\
\hspace*{0.6cm} - Deployment of Spacebel Continuous Integration System \\
\hspace*{0.6cm} - Design and deployment of Spacebel Software Development Environment \\
\hspace*{0.6cm} - Maintenance of PROBA-2 flight software \\
\hspace*{0.6cm} - Symmetric Multi-Processing of PROBA-2 flight software \\
\hspace*{0.6cm} - Radio Frequency Interference of VNREDSAT-1B - Preliminary study \\
\hspace*{0.6cm} - Time and space partitioning of PROBA-2 Flight Software (R\&D) \\
\hspace*{0.6cm} - In-flight hosting of prototype application \\
\hspace*{0.6cm} - TARANIS boot software, definition and deployment of the complete validation test bench \\
\hspace*{0.6cm} - TARANIS boot software, involved from proposal, architecture, design to validation tests \\
\hspace*{0.6cm} - Software Validation Facility architecture of Lunar Lander (phase B) \\
\hspace*{0.6cm} - Assessment and acceptance of model based development tools in the scope of a high integrity autonomous \\
\hspace*{0.85cm} rendez-vous and docking control system for ORCSAT study \\
\hspace*{0.6cm} - Operational tests of PROBA-V OBSW \\
\hspace*{0.6cm} - Refactoring of Graphical User Interface of Vega OBC Simulator \\
\hspace*{0.6cm} - Validation of Vegetation Instrument Manager of PROBA-V \\
\hspace*{0.6cm} - Simulation of Mass Memory Unit of PROBA-V \\
\hspace*{0.6cm} - Simulation of Vegetation Instrument of PROBA-V \\
\hspace*{0.6cm} - Coding \& testing of Mass Memory drivers of PROBA-V OBSW \\
\hspace*{0.6cm} - Support, maintenance, integration, validation \& qualification of Expert OBSW \\
\hspace*{0.6cm} - Coding \& testing of Power Conditioning and Distribution Unit of Expert OBSW \\
\hspace*{0.6cm} - Coding \& testing of the Timeline Generator and Post Flight Analysis tools of Expert mission \\
\hspace*{0.6cm} - Coding of the Functional Validation Facility of Expert (European EXPErimental Re-entry Test-bed) \\
\vspace{0.3cm} 

\header{Publications}
2017 : Bits and Chips, Vluchtsoftware: van commerciale ontwikkeltooling naar opensource \\
2016 : \href{https://eclipse.org/papyrus/resources/spacebel-usecasestory.pdf}{CEA, Eclipse Papyrus Case Study Series - Spacebel}. \\
2015 : J. Hardy, A. Bourdoux, D. Torette, P. Parisis, G. Campos Garrido - From napkin sketches to flight software. \\
2014 : J. Hardy, T. Laroche, P. Creten, P. Parisis, M. Hiller - Experimenting maintenance of flight software in an
\hspace*{0.95cm} integrated modular avionics for space. \\
\vspace{0.3cm} 

\header{Eclipse Foundation}
2017 : Project Leader of the Open Source project Eclipse UML Generators. \\
2015 : Eclipse \href{https://projects.eclipse.org/projects/modeling.umlgen}{umlgen project}:
Author of the \href{http://wiki.eclipse.org/Category:Eclipse_UML_Generators/Specification/EmbeddedCGenerator/Contribution}{UML to Embedded C Generator}.\\
2014 : \href{https://projects.eclipse.org/user/3596}{Eclipse Committer}.\\
\end{document}
